Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-05-08 exp1/iswc2013.tex
note bonferroni problem
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@524 43ef1190-90fd-4dd7-a769-d0121f02b80e
overall hypothesis test
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@525 43ef1190-90fd-4dd7-a769-d0121f02b80e

\todo{finish the t-test stuff once ready}

>>>>

The presence of inactive factors makes it possible to use a standard
t-test by averaging the inactive factors for each combination of
control and environmental factors. This enables us to treat our
experiment as a $2^5$ experiment replicated 8 times.

We then extract two vectors, one for the each of the implementations,
and then perform a one-sided hypothesis test where $H_0$ is that they
are equal and $H_1$ is that the vector representing the new
implementation is smaller. In this example, we find that the available
data supports the assertion that the new implementation is better with a
high probability, $p=2.9 \cdot 10^{-10}$.\todo{rationale could be stronger}

For future larger experiments, one must investigate whether it is
necessary to adjust the p-value due to the larger numbers of
hypotheses tested.
